---
title: "The largest beer producing countries in the world in 2018"
author: "Rebeca Viveros"
date: "15/12/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Ranking
In this presentation we show the top 10 largest beer producing countries in 2018. 

In that year, China was the 1st place in the production of this alcoholic beverage, Germany was the first Europe country in the list. 

The numbers are given in millions of hectoliters.

For more details see <https://es.statista.com/estadisticas/1147467/lideres-produccion-cerveza-mundial/>.

*hectoliter: Measure of volume, which is equal to 100 liters.*


## Map with the 10 countries 
If you click the flag, you can see the country and number of hectoliters.

```{r echo=FALSE}
library(leaflet)

China <- makeIcon(
  iconUrl = "https://www.flaticon.es/svg/static/icons/svg/323/323363.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

UnitedStates <- makeIcon(
  iconUrl = "https://www.flaticon.es/svg/static/icons/svg/323/323310.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

Brazil <- makeIcon(
  iconUrl = "https://www.flaticon.es/svg/static/icons/svg/3909/3909370.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

Mexico <- makeIcon(
  iconUrl = "https://www.flaticon.es/svg/static/icons/svg/206/206600.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

Germany <- makeIcon(
  iconUrl = "https://www.flaticon.es/svg/static/icons/svg/323/323332.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

Russia <- makeIcon(
  iconUrl = "https://www.flaticon.es/svg/static/icons/svg/323/323300.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

Japan <- makeIcon(
  iconUrl = "https://www.flaticon.es/svg/static/icons/svg/197/197604.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

Vietnam <- makeIcon(
  iconUrl = "https://www.flaticon.es/svg/static/icons/svg/197/197473.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

UnitedKigdom <- makeIcon(
  iconUrl = "https://www.flaticon.es/svg/static/icons/svg/323/323329.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

Poland <- makeIcon(
  iconUrl = "https://www.flaticon.es/svg/static/icons/svg/197/197529.svg",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

iconSet <- iconList(China= China,
                    UnitedStates = UnitedStates,
                    Brazil = Brazil,
                    Mexico = Mexico,
                    Germany = Germany,
                    Russia = Russia,
                    Japan = Japan,
                    Vietnam = Vietnam,
                    UnitedKigdom = UnitedKigdom,
                    Poland = Poland)

TopCountries <- data.frame(country = c("China", "UnitedStates", "Brazil", "Mexico", 
                                       "Germany","Russia","Japan","Vietnam","UnitedKigdom",
                                       "Poland"),
                           lat = c(39.9075,38.89511,-23.5475,19.42847,52.52437,62.965840,35.35,14.058324,55.378051,	51.919438),
                           lng = c(116.39723,-77.03637,-46.63611,-99.12766,13.41053,95.522021,137.18333,108.277199,-3.435973,19.145136),
                           prod = c(381.2, 214.61, 141.38, 119.8, 93.65, 77.47, 52.64, 43, 41.53,40.93))

TopCountries %>%
  leaflet() %>%
  addTiles() %>%
  addProviderTiles(providers$Esri.NatGeoWorldMap) %>%
  addMarkers(~lat, lng = ~lng, icon = ~iconSet[country],
             popup = paste(sep = "<br/>", TopCountries$country, TopCountries$prod))
```

## To be clear
This graph shows the ranking most clearly.

```{r echo=FALSE}
library(ggplot2)

g <- ggplot(TopCountries, aes(x = reorder(country, +prod), y = prod)) +
  geom_bar(stat = "identity", fill=rgb(0.1,0.4,0.5,0.7)) +
  ggtitle("The largest beer producing countries in the world in 2018") +
  coord_flip() +
  xlab(" ") + ylab(" ")
g
```


## Just viewing the data
We can see the numbers in this table.
```{r echo=FALSE}
library(knitr)
r <- cbind(TopCountries$country, TopCountries$prod)
kable(r, col.names = c("Country", "hectoliters (in millions)"),align = 'c')

```

## Last but not least
- You can see the code of this work in the next link <https://github.com/BecaVILo/DevelopingDataProducts/blob/main/UsingLeaflet.R>.

- The code for the Rmarkdown document is in <>.


