---
title: "Final Project"
author: "Rebeca Viveros"
date: "18/12/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## How to use this app...

In this app you will be able to predict the price of the index of your election.

### But Fisrt, what is an INDEX?

An index is an indicator or measure of something, and in finance, it typically refers to a statistical measure of change in a securities market. In the case of financial markets, stock, and bond market indices consist of a hypothetical portfolio of securities representing a particular market or a segment of it.

## The Index you can choose are...

- German Stock Index (DAX)
- The Swiss Market Index (SMI)
- Cotation Assistée en Continu (CAC)
- The Financial Times Stock Exchange 100 Index (FTSE)

You can do 5 to 50 predictions. 

## Working with...
To develop this app, we used the EuStockMarkets dataset in R which contains 1860 rows.
```{r echo=FALSE}
library(knitr)
kable(head(EuStockMarkets),align = 'c')
```

## To make the prediction...
To make the prediction we used the `forecast` library. Firts we adjust an ARIMA model, then we did the prediction.

***
For example, if you choose FTSE you would obtain
```{r warning=FALSE,message=FALSE}
library(forecast)
mod1 <- auto.arima(EuStockMarkets[,4]) 
summary(mod1)
```

## Shiny App
```{r fig.align='center', message=FALSE,warning=FALSE}
library(imager)
myimg <- load.image("ShinyApp.JPG")
plot(myimg)
```

